---
title: "final"
author: "YUE LIU"
date: "10/18/2020"
output: html_document
---

#orginal data: select data
```{r}
library(tidyverse)
data <- read.csv("~/Desktop/sta304 ps2/gss.csv")



#choose data 
data1 <- data %>% select(2,3,5,11,12,19,22,23,28,30,38, 41, 42, 48, 49)



reg <- lm(feelings_life ~ age + total_children + age_first_child + sex + province + marital_status + aboriginal + education + living_arrangement + average_hours_worked + self_rated_health + self_rated_mental_health + income_respondent + occupation, data = data1)

summary(reg)

```


####Firstly, we use the ratio likelihood test to test the variables 

#varibles that could not be delete: age, total number of children,income  
```{r}
#install.packages('lmtest')

library(lmtest)

reg_age_delete <- lm(feelings_life ~ total_children+age_first_child+sex+province+marital_status+aboriginal+education+living_arrangement+average_hours_worked + self_rated_health + self_rated_mental_health +income_respondent + occupation, data = data1)





reg_total_children_delete <- lm(feelings_life ~ age+age_first_child+sex+province+marital_status+aboriginal+education+living_arrangement+average_hours_worked + self_rated_health + self_rated_mental_health +income_respondent + occupation, data = data1)





reg_income_delete<- lm(feelings_life ~ age+total_children+age_first_child+sex+province+marital_status+aboriginal+education+living_arrangement+average_hours_worked+self_rated_health+self_rated_mental_health+occupation, data = data1)






lrtest(reg,reg_age_delete)

lrtest(reg,reg_total_children_delete)

lrtest(reg,reg_income_delete)



```
Age,total number of children,income could not be delete because their p-value of the ratio likelihood test are all greater than 0.05 which means that the reg_age_delete, reg_total_children_delete, reg_income_delete are worse than the orginal data. This indicates that in our best fit model, we should contain age, total number of children and income. 


#variables that could be delete: sex, living_arrangement, province
```{r}

library(lmtest)


reg_sex_delete <- lm(feelings_life ~ age+total_children+age_first_child+province+marital_status+aboriginal+education+living_arrangement+average_hours_worked+self_rated_health+self_rated_mental_health+income_respondent+occupation, data = data1)


reg_delete_living_arrangement <- lm(feelings_life ~ age+total_children+age_first_child+sex+province+marital_status+aboriginal+education+average_hours_worked+self_rated_health+self_rated_mental_health+income_respondent+occupation, data = data1)


reg_delete_province<- lm(feelings_life ~ age+total_children+age_first_child+sex+marital_status+aboriginal+education+average_hours_worked+self_rated_health+self_rated_mental_health+income_respondent+occupation, data = data1)



lrtest(reg,reg_sex_delete)
lrtest(reg,reg_delete_living_arrangement)
lrtest(reg,reg_delete_province)





```
Sex, living_arrangement,province could be delete because their p-value are both smaller than 0.05 which means that the reg_sex_delete, reg_delete_living_arrangement are better than the orginal data according to the ratio likelihood test. This indicates that in our best fit model, we may consider to not contain sex, living_arrangement, province. 


## Variables that contain NA data values:age_first_child, marital_status, aboriginal,education,average_hours_worked,self health, self mental health,occupation
In fact, Many variables (i.e age_first_child, marital_status, aboriginal,education,average_hours_worked,self health, self mental health,occupation) in our data set that contains special meaning of NA that could not be removed. It results in the inconsistency in the quantity of various variables and is unable to run the likelihood ratio test in order to do variable selection. We decide to keep those variables in our best fit model temporataly. We will use other method to decide whether or not choose these variables in our best fit model. 



# To conclude the above info, the temporary best fit model after ratio likelihood test:
```{r}
reg <- lm(feelings_life ~ age+total_children+age_first_child+sex+province+marital_status+aboriginal+education+living_arrangement+average_hours_worked+self_rated_health+self_rated_mental_health+income_respondent+occupation, data = data1)


reg_finaltem<-lm(feelings_life ~ age+total_children+age_first_child+marital_status+aboriginal+education+average_hours_worked+self_rated_health+self_rated_mental_health+occupation, data = data1)

lrtest(reg, reg_finaltem)
summary(reg_finaltem)
```

We deleted the sex, living_arrangement, province varibles and named it as the reg_finaltem. 
From the ratio likelihood test, we could see the p-value is less than 0.05 which means the second model(the reg_finaltem) is better than the original model which is also a sign that help us to make sure the model is temporary the best fit. 



#use the summary of reg_finaltem to deal with the NA terms:
```{r}
summary(reg_finaltem)

reg_finaltem<-lm(feelings_life ~ age+total_children+age_first_child+marital_status+aboriginal+education+average_hours_worked+self_rated_health+self_rated_mental_health+occupation, data = data1)

#delete aboriginal, education, average_hours_worked,occupation

reg_final<-lm(feelings_life ~ age+total_children+age_first_child+marital_status+self_rated_health+self_rated_mental_health, data = data1)
#summary(reg_final)
```
From the summary of the reg_fianltem, we could see that the p-value of the aboriginal, education, average_hours_worked,occupation
